---
title: "ICA experiment diagnostics"
author: "Alexander Mangulad Christgau"
output: knitr:::html_vignette
---

This markdown document examines results from experiments of Independent Component Analysis applied on EEG data, and accompanies a project on the aforementioned.


```{r setup, include=FALSE}
#Load packages
library(ggplot2)   ## Grammar of graphics
library(reshape2)  ## Reshaping data frames
library(gridExtra) ## ... and more graphics
library(xtable)    ## LaTeX formatting of tables
library(plyr)
```

Load data
```{r}
SVMdata<- read.csv(file = 'SVM2.csv')
```


Compute standard deviations
```{r}
ag <- aggregate(. ~ Method:n_train, SVMdata, function(x) c(sd = sd(x)))
sp<-ggplot(ag, aes(x=n_train, y=Accuracy, color=Method)) + geom_smooth() + 
  labs(x = "Number of training subjects", y = "Standard deviation of prediction accuarcy")
sp
```

Fit simple linear model with main effects
```{r}
mod1 <- glm(Accuracy~Method + n_train, data = SVMdata)
summary(mod1)
plot(mod1)
xtable(mod1)
```

Diagnostics plots for residuals:
```{r}
resids <- function(glmmod){
  p1 <- qplot(fitted(glmmod), residuals(glmmod), alpha =I(.5)) + 
    geom_smooth() + xlab("Fitted values") + ylab("Residuals")
  p2 <- qplot(residuals(glmmod), geom = "histogram") + 
    xlab("residuals")
  p3 <- qplot(sample=rstandard(glmmod), geom = "qq") + geom_abline(slope=1, intercept = 0) +
    xlab("QQ-plot")
  grid.arrange(p1,p2,p3,ncol=3)
}
resids(mod1)
```


Other model could also be considered, but it does not make too much sense to do advanced statistical analysis on the results.
